\input{preamble}
\title{Ymir}
\begin{document}
\maketitle
\tableofcontents

\chapter*{Topology and bornology}\label{chap-topology}

\section{Introduction}\label{sec-introduction-Topology}

In the whole project, a neighbourhood in a topology space is taken in Bourbaki's sense. In particular, a neighbourhood is not necessarily open.

We follow Bourbaki's convention about compact space. A comapct space is always Hausdorff. 

On the other hand, we do not require locally compact spaces and paracompact spaces be Hausdorff.

A connected topological is always non-empty.

References to this chapter include \cite{Berk93}.

\section{Nets}\label{sec-nets}

Let $X$ be a set, $Y\subseteq X$ be a subset. Consider a collection $\tau$ of subsets of $X$, we write
\[
    \tau|_Y:=\left\{V\in \tau: V\subseteq Y \right\}.    
\]

\begin{definition}
    Let $X$ be a topology space and $\tau$ be a collection of subsets of $X$. We say $\tau$ is
    \begin{enumerate}
        \item \emph{dense} if for any $V\in \tau$ and any $x\in V$, there is a fundamental system of neighbourhoods of $x$ in $V$ consisting of sets from $\tau|_V$;
        \item a \emph{quasi-net} on $X$ if for each $x\in X$, there exist $n\in \mathbb{Z}_{>0}$, $V_1,\ldots,V_n\in \tau$ such that $x\in V_1\cap \cdots\cap V_n$ and that $V_1\cup\cdots\cup V_n$ is a neighbourhood of $x$ in $X$;
        \item a \emph{net} on $X$ if it is a quasi-net and if for any $U,V\in \tau$, $\tau|_{U\cap V}$ is a quasi-net on $U\cap V$;
        \item \emph{locally finite} if for any $x\in X$, there is a neighbourhood $U$ of $x$ in $X$ such that $\{V\in \tau:V\cap U\neq \emptyset\}$ is finite.
    \end{enumerate}
\end{definition}
We observe that if $\tau$ is a net, $\tau|_{U\cap V}$ is in fact a net.

\begin{lemma}\label{lma-quasinetopenset}
    Let $X$ be a topological space and $\tau$ be a quasi-net on $X$. 
    \begin{enumerate}
        \item A subset $U\subseteq X$ is open if and only if for each $V\in \tau$, $U\cap V$ is open in $V$.
        \item Suppose that $\tau$ consists of compact sets. Then $X$ is Hausdorff if and only if for any $U,V\in \tau$, $U\cap V$ is compact.
    \end{enumerate}
\end{lemma}
We remind the readers that a compact space is Hausdorff by our convention.
\begin{proof}
    (1) The direct implication is trivial. Suppose that $U\cap V$ is open in $V$ for all $V\in \tau$. We want to show that $U$ is open. Take $x\in U$, we can find $n\in \mathbb{Z}_{>0}$, $V_1,\ldots,V_n\in \tau$ all containing $x$ such that $V_1\cup \cdots \cup V_n$ is a neighbourhood of $x$ in $X$. By our hypothesis, we can find open sets $W_1,\ldots,W_n$ in $W$ such that $W\cap V_i=U\cap V_i$ for $i=1,\ldots,n$. Then $W=W_1\cap \cdots\cap W_n$ is an open neighbourhood of $x$ in $X$. But then
    \[
        U\cap (V_1\cup\cdots\cup V_n)\supseteq W\cap   (V_1\cup\cdots\cup V_n),
    \]
    the latter is a neighbourhood of $x$ hence so is the former. It follows that $U$ is open.

    (2) The direct implication is trivial. Consider the quasi-net $\tau\times\tau:=\{U\times V: U,V\in \tau\}$ on $X\times X$. 
    By (1), it suffices to verify that the intersection of the diagonal with $U\times V$ is closed in $U\times V$  for any $U,V\in \tau$. But this intersection is homeomorphic to $U\cap V$, which is compact by our assumption and hence closed as $U$, $V$ are both Hausdorff.
\end{proof}

\begin{lemma}\label{lma-quasinetimplyloccpt}
    Let $X$ be a Hausdorff space. Assume that $X$ admits a quasi-net $\tau$ consisting of compact sets. Then $X$ is locally compact.
\end{lemma}
\begin{proof}
    Take $x\in X$. By assumption, we can find $n\in \mathbb{N}$ and $V_1,\ldots,V_n\in \tau$ all containing $x$ such that $V_1\cup\cdots\cup V_n$ is a neighbourhood of $x$. This neighbourhood is clearly compact.
\end{proof}

\begin{lemma}
    Let $X$ be a Hausdorff space and $\tau$ be a collection of compact subsets of $X$. Then the following are equivalent:
    \begin{enumerate}
        \item $\tau$ is a quasi-net;
        \item For each $x\in X$, there are $n\in \mathbb{N}$ and $V_1,\ldots,V_n\in \tau$ such that $V_1\cup\cdots\cup V_n$ is a neighbourhood of $x$ in $X$.
    \end{enumerate}
\end{lemma}
\begin{proof}
    (1) $\implies$ (2): This is trivial.

    (2) $\implies$ (1): Given $x\in X$, take $V_1,\ldots,V_n$ as in (2). We may assume that $x\in V_1,\ldots,V_m$ and $x\not\in V_{m+1},\ldots,V_n$ for some $1\leq m\leq n$. Then $V_1\cup\cdots\cup V_m$ is a neighbourhood of $x$ in $X$: if $U$ is an open neighbourhood of $x$ in $X$ contained in $V_1\cup \cdots\cup V_n$, then $U\setminus (V_{m+1}\cup\cdots \cup V_n)$ is an open neighbourhood of $x$ in $X$ contained in $V_1\cup\cdots\cup V_m$.
\end{proof}

\begin{lemma}\label{lma-netproperty1}
    Let $X$ be a topological space and $\tau$ be a net on $X$ consisting of compact sets. Then
    \begin{enumerate}
        \item for any pair $U,V\in \tau$, the intersection $U\cap V$ is locally closed in $U$ and in $V$;
        \item If $n\in \mathbb{Z}_{>0}$, $V,V_1,\ldots,V_n\in \tau$ are such that 
            \[
                V\subseteq V_1\cup \cdots\cup V_n,
            \]
            then there are $m\in \mathbb{Z}_{>0}$ and $U_1,\ldots,U_m\in \tau$ such that 
            \[
                V=U_1\cup\cdots\cup U_m  
            \]
            and each $U_j$ is contained in some $V_i$.
    \end{enumerate}
\end{lemma}
\begin{proof}
    (1) It suffices to show that $U\cap V$ is locally compact in the induced topology. This follows from \cref{lma-quasinetimplyloccpt}.
    
    (2) For each $x\in V$ and each $i=1,\ldots,n$ such that $x\in V_i$, we take a neighbourhood of $x$ in $V\cap V_i$ of the form $W_iV_{i1}\cup\cdots\cup V_{im_i}$ for some $m_i\in \mathbb{Z}_{>0}$ and $V_{ij}\in \tau$ for $j=1,\ldots,m_i$. Then the union of all $W_i$'s is a neighbourhood of $x$ of the form $U_1\cup \cdots U_m$, where $U_j$ belongs to $\tau$ and is contained in some $V_i$. Using the compactness of $V$, we conclude.
\end{proof}

\section{Paracompact spaces}

\begin{definition}
    A topological space $X$ is \emph{paracompact} if any open covering of $X$ admits a locally finite refinement.
\end{definition}
A paracompact space is not necessarily Hausdorff according to our definition.

\begin{proposition}\label{prop-paracptrefinement}
    Let $X$ be a locally compact topological space. 
    \begin{enumerate}
        \item Assume that each connected component of $X$ is $\sigma$-compact, then $X$ is paracompact.
        \item If $X$ is paracompact and Hausdorff, then each connected component of $X$ is $\sigma$-compact.
    \end{enumerate}
    If the conditions in (2) are satisfied, for any basis of neighbourhoods $\mathcal{B}$ of $X$, every open covering $\mathcal{U}$ of $X$ can be refined into a locally finite covering $\mathcal{V}$ consisting of elements in $\mathcal{B}$.
\end{proposition}
We do not assume that the elements in $\mathcal{B}$ be open. The covering $\mathcal{V}$ is not necessarily open.

\begin{thm}[Michael]\label{thm-Michael}
    Let $f:X\rightarrow Y$ be a closed continuous map of topological spaces. Assume that $X$ is paracompact and Hausdorff, then $f(X)$ is also paracompact and Hausdorff.
\end{thm}
This is a classical theorem of Ernest Michael. \textcolor{red}{Reproduce the proof.}

\begin{proposition}
    Let $X$ be a paracompact space and $Y\subseteq X$ be a closed subspace. Then $Y$ is paracompact.
\end{proposition}

\begin{proposition}
    Let $X$ be a locally compact Hausdorff space and $Y\subseteq X$ be a subspace, then the following are equivalent:
    \begin{enumerate}
        \item $Y$ is locally compact and Hausdorff;
        \item $Y$ is a locally closed subspace of $X$.
    \end{enumerate}
    
\end{proposition}

\section{Closed maps and topologically finite maps}

\begin{definition}[{\cite[\href{https://stacks.math.columbia.edu/tag/004E}{Tag 004E}]{stacks-project},\cite[\href{https://stacks.math.columbia.edu/tag/0CY1}{Tag 0CY1}]{stacks-project}}]
    A map $f:X\rightarrow Y$ of topological spaces is \emph{closed} if for each closed subset $Z$ in $X$, $f(Z)$ is closed in $Y$.

    A map $f:X\rightarrow Y$ of topological spaces is \emph{separated} if it is continuous and the diagonal map $\Delta:X\rightarrow X\times_Y X$ is closed.
\end{definition}
A closed map is not necessarily continuous.

\begin{lemma}\label{lma-opennhfiberclosedmap}
    Let $f:X\rightarrow Y$ be a closed map of topological spaces, then for each $y\in Y$ and any open neighbourhood $U$ of $f^{-1}(y)$ in $X$, there is an open neighbourhood $V$ of $y$ in $Y$ such that $f^{-1}(V)\subseteq U$.
\end{lemma}
\begin{proof}
    It suffices to take $V=Y\setminus f(X\setminus U)$,
\end{proof}
\begin{lemma}\label{lma-closedmaprestricttarget}
    Let $f:X\rightarrow Y$ be a closed map of topological spaces. Then for any subspace $V$ of $Y$, the map $f^{-1}(V)\rightarrow V$ induced by $f$ is closed.
\end{lemma}
\begin{proof}
    Let $A$ be a closed subset of $U:=f^{-1}(V)$. We need to show that $f(A)$ is closed in $V$. Choose a closed subset $B$ of $X$ such that $A=B\cap U$, then $f(B)$ is closed in $Y$ and $f(A)=f(B)\cap V$ is closed in $V$.
\end{proof}

\begin{definition}
    A $f:X\rightarrow Y$ of topological spaces is \emph{topologically finite} if 
    \begin{enumerate}
        \item $f$ is separated and closed;
        \item for each $y\in Y$, the set $f^{-1}(y)$ is finite.
    \end{enumerate}

    A map $f:X\rightarrow Y$ of topological spaces is \emph{topologically finite at $x\in X$} if there is an open neighbourhood $U$ of $x$ in $X$ and an open neighbourhood $V$ of $f(x)$ in $Y$ such that $f(U)\subseteq V$ and the induced map $U\rightarrow V$ is topologically finite.
\end{definition}

\begin{proposition}\label{prop-topfinitechar}
    Let $f:X\rightarrow Y$ be a map of topological spaces. Then the following are equivalent:
    \begin{enumerate}
        \item $f$ is topologically finite;
        \item $f$ is proper and all fibers of $f$ are discrete.
    \end{enumerate}
\end{proposition}
Here the properness is defined as in \cite[\href{https://stacks.math.columbia.edu/tag/005O}{Tag 005O}]{stacks-project}. In particular, a proper map is always separated and hence continuous.
\begin{proof}
    Assume that $f$ is topologically finite. As the fibers of $f$ are finite and Hausdorff, they are discrete.
    We need to show that $f$ is proper. This follows from \cite[\href{https://stacks.math.columbia.edu/tag/005R}{Tag 005R}]{stacks-project}.

    Conversely, assume that $f$ is proper with discrete fibers. By \cite[\href{https://stacks.math.columbia.edu/tag/005R}{Tag 005R}]{stacks-project} again, the fibers of $f$ are compact and hence finite. The map $f$ is closed and separated as it is proper. So (1) follows.
\end{proof}

\begin{lemma}\label{lma-qcpttoHausdorffproper}
    Let $f:X\rightarrow Y$ be a continuous map between topologically spaces. Assume that $Y$ is Hausdorff.
    Let $W$ be an open relative quasi-compact subset of $X$, then the map
    \[
        W\setminus f^{-1}(f(\partial W))\rightarrow Y\setminus f(\partial W)
    \]
    induced by $f$ is proper.
\end{lemma}
\begin{proof}
    It is well-known that $f|_{\bar{W}}:\bar{W}\rightarrow Y$, as a continuous map from a quasi-compact space to a Hausdorff space is proper. The map in the lemma is a base change of the given map, hence is also proper. We apply \cite[\href{https://stacks.math.columbia.edu/tag/005R}{Tag 005R}]{stacks-project}.
\end{proof}

\begin{proposition}
    Let $f:X\rightarrow Y$ be a topologically finite map of topological spaces. Then for any subspace $V\subseteq Y$, the map $f^{-1}(V)\rightarrow V$ induced by $f$ is topologically finite.
\end{proposition}
\begin{proof}
    This follows immediately from \cref{lma-closedmaprestricttarget}.
\end{proof}

\begin{thm}\label{thm-localstructuretopfinitemap}
    Let $f:X\rightarrow Y$ be a topologically finite map of topological spaces. Let $y\in f(X)$ and $x_1,\ldots,x_n$ ($n\in \mathbb{Z}_{>0}$) denote the distinct points of $f^{-1}(y)$. Take pairwise disjoint open neighbourhoods $U_1',\ldots,U_n'$ of $x_1,\ldots,x_n$ in $X$. Then any neighbourhood $V'$ of $y$ in $Y$ contains an open neighbourhood $V$ of $y$ satisfying the following conditions:
    \begin{enumerate}
        \item $U_1:=f^{-1}(V)\cap U_1',\ldots, U_n:=f^{-1}(V)\cap U_n'$ are pairwise disjoint open neighbourhoods of $x_1,\ldots,x_n$ in $X$;
        \item $f^{-1}V=\bigcup_{j=1}^n U_j$;
        \item The maps $U_j\rightarrow V$ for $j=1,\ldots,n$ induced from $f$ are all topologically finite.
    \end{enumerate}

    Let $\mathcal{F}$ be a sheaf of sets on $X$, then we have a functorial bijection
    \[
        f_*\mathcal{F}(V)\cn \prod_{j=1}^n \mathcal{F}(U_j).
    \]
\end{thm}
The existence of $U_1',\ldots,U_n'$ is guaranteed by \cite[\href{https://stacks.math.columbia.edu/tag/0CY2}{Tag 0CY2}]{stacks-project}.
\begin{proof}
    As $\bigcup_{j=1}^n U_j'$ is an open neighbourhood of $f^{-1}(y)$ in $X$, by \cref{lma-opennhfiberclosedmap} and \cref{lma-closedmaprestricttarget}, we can find an open neighbourhood $V\subseteq V'$ of $y$ in $Y$ such that 
    \[
        f^{-1}V\subseteq \bigcup_{j=1}^n U_j'.
    \]
    The conditions (1) and (2) are therefore satisfied.

    In order to prove (3), it remains to show that the induced maps $U_j\rightarrow V$ are closed for $j=1,\ldots,n$. We may take $j=1$.
    Let $A$ be a closed subset of $U_1$. Then $A$ is closed in $f^{-1}(V)$ by (1) and (2). It follows that $f(A)$ is closed in $V$ by \cref{lma-closedmaprestricttarget}.

    The last assertion follows from (1) and (2).
\end{proof}

\begin{corollary}
    Let $f:X\rightarrow Y$ be a topologically finite map of topological spaces. Let $x\in X$ be $U'$  be an open neighbourhood of $x$ in $X$ such that all other points in $f^{-1}(f(x))$ are in the interior of $X\setminus U'$. Then any neighbourhood $V'$ of $f(x)$ in $Y$ contains an open neighbourhood $V$ of $y$ such that for $U:=f^{-1}(V)\cap U'$ the map $g:U\rightarrow V$ induced by $f$ is topologically finite and $g^{-1}(g(x))=\{x\}$.
\end{corollary}
\begin{proof}
    This follows immediately from \cref{thm-localstructuretopfinitemap}.
\end{proof}

\begin{corollary}\label{cor-pushforwardsheaffinite}
    Let $f:X\rightarrow Y$ be a topologically finite map of topological spaces. Let $\mathcal{F}$ be a sheaf of sets on $X$, $y\in f(X)$. Denote by $x_1,\ldots,x_n$ ($n\in \mathbb{Z}_{>0}$) the distinct points of the fiber $f^{-1}(y)$. Then we have a canonical bijection
    \[
        (f_*\mathcal{F})_y\cn \prod_{j=1}^n \mathcal{F}_{x_j}.
    \]
    In particular, $f_*:\AbCat(X)\rightarrow \AbCat(Y)$ is exact.
\end{corollary}
\begin{proof}
    This follows immediately from \cref{thm-localstructuretopfinitemap}.
\end{proof}


\section{Exhaustion}

\begin{definition}\label{def-exhaustion}
    Let $X$ be a space. A \emph{quasi-compact exhaustion}  of $X$ is a sequence of quasi-compact sets $(K_i)_{i\in \mathbb{Z}_{>0}}$ in $X$ such that 
    \begin{enumerate}
        \item For each $i\in \mathbb{Z}_{>0}$,
            \[
                K_i\subseteq \Int K_{i+1};  
            \]
        \item 
            \[
                X=\bigcup_{i=1}^{\infty}K_i.
            \]
    \end{enumerate}
    When $X$ is Hausdorff, we also say $(K_i)_{i\in \mathbb{Z}_{>0}}$ is a \emph{compact exhaustion}.
\end{definition}

\begin{proposition}\label{prop-qcptexhaustion}
    Let $X$ be a topological space. Then the following are equivalent:
    \begin{enumerate}
        \item there is a quasi-compact exhaustion of $X$;
        \item $X$ is $\sigma$-compact and weakly locally compact;
        \item $X$ is Lindelöf and weakly locally compact.
    \end{enumerate}
\end{proposition}
\begin{proof}
    \textcolor{red}{To be included.}
\end{proof}

\begin{proposition}
    Let $X$ be a locally compact Hausdorff topological space admitting a countable basis, then $X$ admits a compact exhaustion.
\end{proposition}
Note that in the book of Grauret--Remmert, the condition of being Hausdorff is omitted.
\begin{proof}
    \textcolor{red}{Include a proof}
\end{proof}

\begin{lemma}\label{lma-exhaustioncoh}
    Let $X$ be a paracompact Hausdorff topological space and $\mathcal{F}$ be a sheaf of Abelian groups on $X$. Let $q\in \mathbb{Z}_{\geq 2}$ and $(K_i)_{i\in \mathbb{Z}_{>0}}$ be a compact exhaustion of $X$ with the following property:
    \[
        H^{q-1}(K_i,\mathcal{F})=H^q(K_i,\mathcal{F})=0  
    \]
    for all $i\in \mathbb{Z}_{>0}$. Then $H^q(X,\mathcal{F})=0$.
\end{lemma}
\begin{proof}
    Grauert--Remmert P103.
\end{proof}

\section{Maps with discrete fibers}

\begin{lemma}\label{lma-connectedcompofiberdim0basis}
    Let $X$ be a locally connected locally compact Hausdorff topological space and $X_0$ be a Hausdorff space with a basis $\beta_0$. Consider a continuous map $f:X\rightarrow X_0$ with discrete fiber. Then there is a basis of $X$ made up of connected components of $f^{-1}U_0$ with $U_0\in \beta_0$.
\end{lemma}
\begin{proof}
    Let $x\in X$ and $V$ be an open neighbourhood of $x$ in $X$. We need to find $U_0\in \beta_0$ and a component $U$ of $f^{-1}(U_0)$ such that $U\subseteq V$.
    
    For this purpose, we may assume that $X$ is connected. Set $x_0=f(x)$.
    Choose an open neighbourhood $W$ of $x$ in $V$ with $\bar{W}$ compact and $B\cap f^{-1}(x_0)=\emptyset$, where $B=\bar{W}\setminus W$. Let $B_0=f(B)$, then $x_0\not\in B_0$. As $B_0$ is compact, we can find $U_0\in \beta_0$ containing $x_0$ such that $B_0\cap U_0=\emptyset$. Let $U$ be the connected component of $f^{-1}(U_0)$ containing $x$. Then $B\cap U=\emptyset$ and hence $U\subseteq W\cup (X\setminus \bar{W})$. As $X$ is connected and $W\cap U$ is non-empty, we find that $U\subseteq W$.
\end{proof}

\begin{proposition}\label{prop-fiberdiscountablebasisinh}
    Let $X$ be a connected, locally connected, first countable, locally compact Hausdorff space and $X_0$ be a topological space with countable basis. If there is a map $f:X\rightarrow X_0$ with discrete fibers, then $X$ has countable topology as well.
\end{proposition}
This result is proved in \cite{Jur59}.

\begin{proof}
    Let $\beta_0$ be a countable basis for the topology on $X_0$. Let $\beta$ be the collection of open sets $U$ in $X$ such that
    \begin{enumerate}
        \item There is $U_0\in \beta_0$ such that $U$ is a connected component of $f^{-1}(U_0)$;
        \item $U$ is relatively compact in $X$.
    \end{enumerate}
    By our assumption, any $U\in \beta$ has countable basis. By \cref{lma-connectedcompofiberdim0basis}, $\beta$ is a basis for the topology on $X$. It remains to show that $\beta$ is countable.

    Let $V\in \beta$. For each $n\in \mathbb{Z}_{>0}$, $\beta^{(n)}$ denotes the collection of $U\in \beta$ with the following property: there is a map $\{1,\ldots,n\}\rightarrow \beta$, say assigning $U_i\in \beta$ to $i$ such that $U_1=V$, $U_i\cap U_{i+1}\neq \emptyset$ for $i=1,\ldots,n-1$. As $X$ is connected,
    \[
        \beta=\bigcup_{n=1}^{\infty}\beta^{(n)}.  
    \]
    It remains to show that for each $n\in \mathbb{Z}_{>0}$, $\beta^{(n)}$ is countable. We make an induction. The case $n=1$ is obvious. Assume that $n\geq 2$ and the assertion has been proved for $n-1$. Let $U_0\in \beta_0$ and $U'\in \beta^{(n-1)}$. Let $\alpha^{(n)}(U_0,U')$ denote the collection of $U\in \beta^{(n)}$ such that $U$ is a connected component of $f^{-1}(U_0)$ and $U\cap U'$ is non-empty. Then
    \[
        \beta^{(n)}=\bigcup_{U_0\in \beta_0,U'\in \beta^{(n-1)}}\alpha^{(n)}(U_0,U').  
    \]
    But each $\alpha_{(n)}(U_0,U')$ is countable as $U'$ has countable basis. It follows that $\beta^{(n)}$ is countable.
\end{proof}

\section{Previlaged neighbourhoods}
\begin{definition}
    Let $X$ be a topological space, $x\in X$ and $\mathcal{F}$ be a sheaf of sets on $X$. We say a neighbourhood $U$ of $x$ in $X$ is \emph{$\mathcal{F}$-previlaged at $x$} if the map
    \[
        H^0(U,\mathcal{F})\rightarrow \mathcal{F}_x  
    \]
    is injective. We also say $U$ is an \emph{$\mathcal{F}$-previlaged neighbourhood} of $x$ in $X$.
\end{definition}

\begin{proposition}\label{prop-previalsequence}
    Let $X$ be a topological space, $x\in X$ and 
    \[
        0\rightarrow \mathcal{G}\rightarrow \mathcal{F}\rightarrow \mathcal{H}
    \]
    be an exact sequence of sheaves of Abelian groups on $X$. Let $U$ be a neighbourhood of $x$ in $X$.
    \begin{enumerate}
        \item If $U$ is $\mathcal{G}$-previlaged at $x$ and $\mathcal{H}$-previlaged at $x$, then it is $\mathcal{F}$-previlaged at $x$;
        \item If $U$ is $\mathcal{F}$-previlaged at $x$, then it is $\mathcal{G}$-previlaged at $x$.
    \end{enumerate}
\end{proposition}
\begin{proof}
    We have a commutative diagram of $\mathbb{C}$-linear spaces
    \[
        \begin{tikzcd}
            0 \arrow[r] & {H^0(X,\mathcal{G})} \arrow[r] \arrow[d] & {H^0(X,\mathcal{F})} \arrow[r] \arrow[d] & {H^0(X,\mathcal{H})} \arrow[d] \\
            0 \arrow[r] & \mathcal{G}_x \arrow[r]                  & \mathcal{F}_x \arrow[r]                  & \mathcal{H}_x                 
        \end{tikzcd}.
    \]
    Both assertions follow from simple diagram chasing.
\end{proof}
\section{Stratification}



\begin{definition}
    Let $M$ be a real analytic manifold and $\Omega$ be an open subset of $M$. A \emph{stratification} $\mathcal{N}$ of $\Omega$ is a finite collection of connected locally closed analytic submanifold of $\Omega$ such that
    \begin{enumerate}
        \item $\Omega$ is a disjoint union of the elements in $\mathcal{N}$;
        \item for each $\Gamma\in \mathcal{N}$, $(\bar{\Gamma}\setminus \Gamma)\cap \Omega$ is the union of elements in $\mathcal{N}$ of strictly smaller dimensions.
    \end{enumerate}
    Elements in $\mathcal{N}$ are called the \emph{strata} of the stratification.

    For each open subset $U\subseteq \Omega$, we write $\mathcal{N}(U)$ for the collection of subsets of $U$ consisting of all connected components of $U\cap \Gamma$ for all $\Gamma\in \mathcal{N}$.

    Take $x\in \Omega$, an open neighbourhood $U$ of $x$ in $\Omega$ is \emph{normal} with respect to $\mathcal{N}$ if 
    \begin{enumerate}
        \item $\mathcal{N}(U)$ is a stratification of $U$;
        \item for each $\Gamma\in \mathcal{N}(U)$, $x\in \bar{\Gamma}$.
    \end{enumerate}
\end{definition}

\begin{definition}
    Let $X$ be a real analytic space. For each $x\in X$, we temporarily write $\mathcal{J}_a$ for the smallest family of germs of analytic subspaces of $X$ stable under finite union, finite intersection, complement and contains all germs of the form $\{f<0\}_a$ for some $f\in \mathcal{O}_{X,x}$.

    A subset $A$ of $X$ is \emph{real semi-analytic} if for all $x\in X$, $A_x\in \mathcal{J}_x$.
\end{definition}

\begin{thm}\label{thm-refinesemianatostratification}
    Let $X$ be a real analytic manifold, $x\in X$. Suppose that $\{A_0,\ldots,A_m\}$ is a finite collection of real semi-analytic subsets of $X$. Then there is a stratification $\mathcal{N}$ of an open neighbourhood $U$ of $x$ in $X$ compatible with $A_i$ in the sense that each stratum is either contained in $A_i$ or is disjoint from $A_i$ for $i=1,\ldots,m$ such that each $y\in U$ admits a fundamental system of normal neighbourhoods with respect to $\mathcal{N}$.
\end{thm}
\begin{proof}
    \textcolor{red}{Include the ref.}
\end{proof}


\begin{proposition}\label{prop-fundamentalsysmopnhprevi}
    Let $X$ be a real analytic space, $A$ be a semi-analytic set in $X$, $x\in A$. Let $Y_1,\ldots,Y_m$ be finitely many analytic sets in $X$ passing $x$. Then there is a fundamental system $\mathcal{B}$ of neighbourhoods of $a$ in $A$ such that for each $V\in \mathcal{B}$, there is a fundamental system $\mathcal{B}_V$ of open neighbourhoods of $V$ in $X$ so that for any $W\in \mathcal{B}_V$, $W\cap Y_i$ is $\mathcal{O}_{Y_i}$-previlaged at $x$ for $i=1,\ldots,m$.
\end{proposition}
\begin{proof}
    The problem is local on $X$, we may assume that $X=\mathbb{R}^n$ for some $n\in \mathbb{N}$ and $x=0$. Let $U$ be an open neighbourhood of $0$ in $\mathbb{R}^n$ compatible with the collection $\{A,Y_1,\ldots,Y_m\}$ and such that each $y\in U$ admits a fundamental system $\mathcal{U}(x)$ of normal neighbourhoods with respect to $\mathcal{N}$. The existence of $U$ is guaranteed by \cref{thm-refinesemianatostratification}.
    Let
    \[
        \mathcal{B}=\left\{Q\cap A: Q\in \mathcal{U}(0)\right\}.  
    \]
    Suppose $V\in \mathcal{B}$, say $B=Q\cap A$ with $Q\in \mathcal{U}(0)$. 
    
    Let $\Omega$ be a neighbourhood of $V$ in $\mathbb{R}^n$, we need to construct an open neighbourhood $W$ of $V$ in $\mathbb{R}^n$ contained in $\Omega$ such that $W\cap Y_i$ is $\mathcal{O}_{Y_i}$-previlaged at $x$ for $i=1,\ldots,m$.

    For each $y\in V$, we let $Q(y)$ be an open neighbourhood of $x$ in $\mathbb{R}^n$ normal with respect to $\mathcal{N}$ and contained in $\Omega$.
    Let $W=\bigcup_{x\in V}Q(x)$.

    Fix $i\in \{1,\ldots,m\}$. We will verify that $W\cap Y_i$ is $\mathcal{O}_{Y_i}$-previlaged at $x$.

    Let $f\in \mathcal{O}_{Y_i}(W\cap Y_i)$ assume that $f$ vanishes in a neighbourhood of $0$, then we claim that $f=0$ on $W\cap Y_i$. Now $Y_i\cap Q$ is a finite union of strata of $\mathcal{N}(Q)$ which are connected manifolds whose closures contain $0$ and either contained in or disjoint from $A$. It is clear that $f$ vanishes on all strata contained in $A\cap Y_i\cap Q$, hence on $A\cap Y\cap  Q$. Also, $f$ vanishes on $Y\cap Q(0)$, so it remains to prove that if $b\in V$, $b\neq 0$, then $f$ vanishes on $Y\cap Q(b)$. 

    Let $\Gamma$ be a stratum of $\mathcal{N}(Q(b))$ contained in $Y$. Then $b\in \bar{\Gamma}$. Take a stratum $\Gamma'$ of $\mathcal{N}(Q)$ so that $\Gamma$ is a connected component of $Q(b)\cap \Gamma'$. We may assume that $b$ is on the boundary of $A$ and $\Gamma'\cap A=\emptyset$. As $A\cap \Gamma\cap Q(b)$ is a union of strata of $\mathcal{N}(Q(b))$, one of them, say $\Gamma_1$ contains $b$. It is the intersection of a stratum $\Gamma_1'$ of $\mathcal{N}(Q)$ with $Q(b)$. Let $C$ be the connected component of $\Gamma'\cap W$ containing $\Gamma$. Consider the set
    \[
        E=\left\{ x\in \Gamma_1'\cap V : \Gamma'_{1,x}\subseteq \overline{C_x} \right\}.    
    \]
    Then $b\in E$ as $\Gamma_1'\cap Q(b)\subseteq \bar{\Gamma}\cap Q(b)\subseteq \bar{C}\cap Q(b)$. Moreover, $E$ is an open subset of $\Gamma_1'\cap V$ by definition. We claim that $E$ is also closed. 
    
    Let us postpone the proof of the claim. As $\Gamma_1'$ is connected, we have $E=\Gamma_1'\cap V$. So 
    \[
        \Gamma_1'\cap V\subseteq \bar{C}\cap V  
    \]
    and 
    \[
        \Gamma_1'\cap W\subseteq \bar{C}\cap W.
    \]
    But $a\in \overline{\Gamma_1}$, so $a\in \bar{C}$ and $f$ vanishes on a clopen subset of $C$, namely $Q(a)\cap C$, so $f$ vanishes on $C$. In particular on $\Gamma$.
    
    
    It remains to verify the claim.
    In fact, we show that if $y\in \bar{E}\cap \Gamma_1'\cap V$, then $\Gamma_1'\cap Q(y)\subseteq \bar{C}\cap Q(y)$. To see this, observe that there is $z\in E\cap Q(y)$, so there is a non-empty open subset of $\Gamma_1'\cap Q(y)$ contained in $\bar{C}\cap Q(y)$. But $\Lambda\cap Q(y)$ is a stratum of $\mathcal{N}(Q(y))$ as $y\in \Gamma_1'$, our claim follows since $\bar{C}\cap Q(y)$ is a union of strata of $\mathcal{N}(Q(y))$.
\end{proof}


\section{Bornology}
\begin{definition}
    Let $X$ be a set. A \emph{bornology} on $X$ is a collection $\mathcal{B}$ of subsets of $X$ such that
    \begin{enumerate}
        \item For any $x\in X$, there is $B\in \mathcal{B}$ such that $x\in \mathcal{B}$;
        \item For any $B\in \mathcal{B}$ and any subset $A\subseteq B$, $A\in \mathcal{B}$;
        \item $\mathcal{B}$ is stable under finite union.
    \end{enumerate}

    The pair $(X,\mathcal{B})$ is called a \emph{bornological set}. The elements of $\mathcal{B}$ are called the \emph{bounded subsets} of $(X,\mathcal{B})$. When $\mathcal{B}$ is obvious from the context, we omit it from the notations.
    
    A morphism between bornological sets $(X,\mathcal{B}_X)$ and $(Y,\mathcal{B}_Y)$ is a map of sets $f:X\rightarrow Y$ such that for any $A\in \mathcal{B}_X$, $f(A)\in \mathcal{B}_Y$. Such a map is called a \emph{bounded map}.
\end{definition}
\begin{definition}
    Let $(X,\mathcal{B})$ be a bornological set. A \emph{basis} for $\mathcal{B}$ is a subset $\mathcal{A}\subseteq \mathcal{B}$ such that for any $B\in \mathcal{B}$, there are $A_1,\ldots,A_n\in \mathcal{A}$ such that $B\subseteq A_1\cup\cdots\cup A_n$.
\end{definition}


\printbibliography
\end{document}